Automatic Amortized Analysis for Imperative Code

### 2014-05-21 paper/main.tex
some notes

>>>>

\section{NOTES}

\subsection{Things to say in the intro}

\paragraph{Quote of Knuth}

\begin{quotation}
  There's even a fundamental gap in the foundations of my main
  mathematical specialty, the analysis of algorithms. Consider, for
  example, a computer program that sorts a list of numbers into
  order. Thanks to the work of Floyd, Hoare, and others, we have
  formal definitions of semantics, and tools by which we can verify
  that sorting is indeed always achieved. My job is to go beyond
  correctness, to an analysis of such things as the program's running
  time: I write down a recurrence, say, which is supposed to represent
  the average number of comparisons made by that program on random
  input data. I'm 100\% sure that my recurrence correctly describes
  the program's performance, and all of my colleagues agree with me
  that the recurrence is "obviously" valid. Yet I have no formal tools
  by which I can prove that my recurrence is right. I don't really
  understand my reasoning processes at all! My student Lyle Ramshaw
  began to create suitable foundations in his thesis (1979), but the
  problem seems inherently difficult. Nevertheless, I don't lose any
  sleep over this situation.
\end{quotation}
http://www.informit.com/articles/article.aspx?p=2213858

\paragraph{Advanteges over previous work}

\begin{itemize}
\item have formal soundness proof with respect to cost semantics
\item can deal with resources that \emph{become available} (e.g, freeing memory) in an execution
\item derive global bounds for the program as a function of the inputs (as opposed to local loop bounds)
\item can handle advance control flow such as break, return, mutual recursive functions
\item do not rely on abstract-interpretation based invariant generation
\item show that constant factors are very precise with respect to the cost semantics
\item demonstrate that the analysis is applicable in the formal verification of system code
\end{itemize}
